\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=1cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

% ---- Section Formatting ----
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

% ================= HEADER =================
\begin{center}
    {\LARGE \textbf{AMIT KUMAR}}\\[2pt]
    Delhi, India \\
    Phone: +91 6307411873 \,|\, 
    Email: \href{mailto:Amitbhardwaj26210@gmail.com}{amitbhardwaj26210@gmail.com} \\
    \href{https://github.com/me-amit2810}{GitHub: me-amit2810} \,|\, 
    \href{https://www.linkedin.com/in/amit2810}{LinkedIn: amit2810}
\end{center}

% ================= OBJECTIVE =================
\section*{Objective}
Motivated B.Tech CSE graduate with strong skills in front-end development, JavaScript, ReactJS, and full-stack concepts. Experienced in building responsive web apps, UI components, and working with APIs. Currently expanding backend development and database knowledge to strengthen full-stack engineering capabilities.

% ================= EDUCATION =================
\section*{Education}
\textbf{B.Tech (Computer Science Engineering)} — Dewan VS Institute of Engineering and Technology \hfill 2021–2025 \\
\textbf{Senior Secondary (Science)} — Jamuna Ram Memorial School (CBSE) \hfill 2020–2021 \\
\textbf{Secondary School} — Suryabadan Vidyapeeth (CBSE) \hfill 2018–2019

% ================= EXPERIENCE =================
\section*{Experience}

\textbf{Frontend Developer — Adkamp Marketing Solutions} \hfill Jan–Feb 2025 \\
\begin{itemize}
    \item Developed the complete frontend of Adkamp’s marketing website using ReactJS.
    \item Built responsive, reusable UI components and optimized performance.
    \item Implemented routing, state handling, API integration, and improved UX flow.
    \item Collaborated with marketing team to meet branding and design requirements.
\end{itemize}

\textbf{Industrial Training — Capgemini Centre of Excellence} \hfill Jul–Sep 2024 \\
\begin{itemize}
    \item Completed hands-on training in AI and Data Science using Python and ML tools.
    \item Worked on data preprocessing, visualization, and ML model development.
\end{itemize}

% ================= PROJECTS =================
\section*{Projects}

\textbf{Next-Gen AI Learning Management System}
\begin{itemize}
    \item Developed an AI-powered LMS with personalized learning paths, analytics, auto-grading, summaries, and doubt-solving.
    \item Technologies: ReactJS, NodeJS, Express, Flask, Hugging Face API, Llama, MySQL, MongoDB, Docker.
\end{itemize}

\textbf{Social Text Sentiment \& Emotion Analysis}
\begin{itemize}
    \item Built an NLP system analyzing 100K+ tweets with ~85\% accuracy for brand and trend monitoring.
    \item Technologies: Python, Flask, NLP models, Hugging Face transformers.
\end{itemize}

\textbf{Interactive Front-End Projects}
\begin{itemize}
    \item Created responsive web apps including BMI Calculator, Color Switcher, Digital Clock, Virtual Keyboard, Number Guessing Game.
    \item Focused on DOM manipulation, events, and interactive UI.
\end{itemize}

% ================= SKILLS =================
\section*{Technical Skills}
\textbf{Programming:} Java, C, Python \\
\textbf{Web-technology:} HTML, CSS (Tailwind), JavaScript, ReactJS, NodeJS \\
\textbf{Database:} SQL \\
\textbf{Tools:} GitHub, Postman, MS Office
% ================= LANGUAGES =================
\section*{Languages}
Hindi (Native), English (Professional)

\end{document}
